Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-26 src/tex/ms.tex
Added script to train the main galaxy flow.

We trained the normalizing flow for \note{N} epochs using the Adam optimizer \citep{adam} with a learning rate of \note{N} to minimize the negative log-likelihood,
\begin{align}
    \mathcal{L} = - \, \mathbb{E}[ \, \log p(x) \, ],
\end{align}
where the expectation is performed over galaxies in the training set and $p(x)$ is defined in Equation \ref{eq:px}.
Training took \note{N} minutes on a Tesla P100 12GB GPU.
The training and test losses can be seen in Figure \note{X}.

>>>>

We trained the normalizing flow for 150 epochs using the Adam optimizer \citep{adam} (with a learning rate of $10^{-3}$, that decreased by a factor of 10 every 50 epochs) to minimize the negative log-likelihood,
\begin{align}
    \mathcal{L} = - \, \mathbb{E}[ \, \log p(x) \, ],
\end{align}
where the expectation is performed over galaxies in the training set and $p(x)$ is defined in Equation \ref{eq:px}.
Training took 7 minutes on a Tesla P100 12GB GPU.
